Kepler's Demographic Cliff: Ages of Young Stars and Planets in the Kepler Field

### 2024-04-28 paper/ms.tex
manual fix nan koi-7368 radius

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=\textwidth]{hist_samples_koi_gyro_ages_hist_field_gyro_ages_20240405_maxage3200.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
		{\bf Kepler's demographic cliff,} visible in the
		rotation-derived ages of stars (left) and planet hosts
		(right) in the Kepler field.
		The 
		light gray histograms correspond to all
		\nuniqstarsantosrotteffcut\
		$T_{\rm eff}\in[3800,6200]\,$K Kepler stars with reported
		rotation periods, and all 
		\nplhoststarwgyroage\ planet-hosting stars with reported
		rotation periods.
		The black histograms impose necessary quality cuts
		on factors such as
		binarity, crowding, and the star's evolutionary state
		( Section~\ref{subsec:flags}).
		In detail, these ``histograms'' are resampled from the posterior
		probability distributions.
		{\bf todo: numbers dont match.  why?}
		\label{fig:hist_tgyro}
	}
\end{figure*}

>>>>

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=\textwidth]{hist_samples_koi_gyro_ages_hist_field_gyro_ages_20240405_maxage3200.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
		{\bf Kepler's demographic cliff,} visible in the
		rotation-derived ages of stars (left) and planet hosts
		(right) in the Kepler field.
		The 
		light gray histograms correspond to all
		\nuniqstarsantosrotteffcut\
		$T_{\rm eff}\in[3800,6200]\,$K Kepler stars with reported
		rotation periods, and all 
		\nplhoststarwgyroage\ planet-hosting stars with reported
		rotation periods.
		The black histograms impose necessary quality cuts
		on factors such as
		binarity, crowding, and the star's evolutionary state
		(Section~\ref{subsec:flags}).
		In detail, these ``histograms'' are resampled from the posterior
		probability distributions.
		{\bf todo: numbers dont match.  why?}
		\label{fig:hist_tgyro}
	}
\end{figure*}
